getlandsat
======

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![Build Status](https://travis-ci.org/ropenscilabs/getlandsat.svg?branch=master)](https://travis-ci.org/ropenscilabs/getlandsat)

`getlandsat`: Get Landsat 8 data from AWS public data sets

## get CRAN and non-CRAN dependencies

```{r eval=FALSE}
install.packages(c("readr", "aws.signature"))
devtools::install_github('cloudyr/aws.s3')
```

## Install

```{r eval=FALSE}
devtools::install_github("ropenscilabs/getlandsat")
```

```{r}
library("getlandsat")
```

## List scenes

```{r}
(res <- lsat_scenes(n_max = 10))
```

## List scene files

```{r}
lsat_scene_files(x = res$download_url[1])
```

## Get an image

Returns path to the image

```{r}
lsat_image(x = "LC80101172015002LGN00_B5.TIF")
```

### Caching

When requesting an image, we first check if you already have that image. If you do, 
we return the path to the file. If not, we get the image, and return the file path.

```{r message=TRUE}
lsat_image(x = "LC80101172015002LGN00_B5.TIF")
```

Note the message given.

See `?lsat_cache` for cache management functions.

## Meta

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
