getlandsat
==========

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "inst/img/"
)
```

[![cran checks](https://cranchecks.info/badges/worst/getlandsat)](https://cranchecks.info/pkgs/getlandsat)
[![Build Status](https://travis-ci.org/ropensci/getlandsat.svg?branch=master)](https://travis-ci.org/ropensci/getlandsat)
[![codecov](https://codecov.io/gh/ropensci/getlandsat/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/getlandsat)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/getlandsat)](https://github.com/metacran/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/getlandsat)](https://cran.r-project.org/package=getlandsat)
[![](https://badges.ropensci.org/58_status.svg)](https://github.com/ropensci/onboarding/issues/58)

`getlandsat`: Get Landsat 8 data from AWS public data sets

`getlandsat` provides access to Landsat <https://landsat.usgs.gov> 8 metadata and images hosted on AWS S3 at <https://registry.opendata.aws/landsat-8/>. The package only fetches data. It does not attempt to aid users in downstream usage, but some additional functionality may be added.

A new function `lsat_search()` lets you search for Landsat images by using the API from Development Seed documented at <https://github.com/sat-utils/sat-api>

Potential users are probably anyone from scientists asking questions about biodiversity or land use change, to software developers creating tools for users to vizualize their data.

## Install

Stable version

```{r eval=FALSE}
install.packages("getlandsat")
```

Dev version

```{r eval=FALSE}
devtools::install_github("ropensci/getlandsat")
```

```{r}
library("getlandsat")
```

## Search for images

```{r eval=FALSE}
x <- lsat_search(collection = "landsat-8", cloud_cover = c(0, 20), limit = 3)$features
names(x)
#> [1] "type"       "properties" "bbox"       "geometry"   "assets"     "links"
x$properties
#>                                         id         c:id                 datetime eo:cloud_cover eo:sun_azimuth
#> 1 LC08_L1TP_183023_20160625_20170323_01_T1 landsat-8-l1 2016-06-25T09:00:16.825Z              0      150.61964
#> 2 LC08_L1TP_183037_20160625_20170323_01_T1 landsat-8-l1 2016-06-25T09:05:51.253Z             19      110.95730
#> 3 LC08_L1TP_183041_20160625_20170323_01_T1 landsat-8-l1 2016-06-25T09:07:26.830Z              0       95.69133
#>   eo:sun_elevation landsat:path landsat:row
#> 1         57.71269          183          23
#> 2         68.16356          183          37
#> 3         68.55517          183          41
```

## List scenes

```{r}
(res <- lsat_scenes(n_max = 10))
```

## List scene files

```{r}
lsat_scene_files(x = res$download_url[1])
```

## Get an image

Returns path to the image

```{r}
lsat_image(x = "LC80101172015002LGN00_B5.TIF")
```

### Caching

When requesting an image, we first check if you already have that image. If you do,
we return the path to the file. If not, we get the image, and return the file path.

```{r message=TRUE}
lsat_image(x = "LC80101172015002LGN00_B5.TIF")
```

Note the message given.

See `?lsat_cache` for cache management functions.

## Visualize

```{r}
library("raster")
x <- lsat_cache_details()[[1]]
img <- raster(x$file)
plot(img)
```

## Meta

* Please [report any issues or bugs](https://github.com/ropensci/getlandsat/issues).
* License: MIT
* Get citation information for `getlandsat` in R doing `citation(package = 'getlandsat')`
* Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). By contributing to this project, you agree to abide by its terms.
