<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{getlandsat introduction}
%\VignetteEncoding{UTF-8}
-->

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.path = "img/"
)
```

getlandsat introduction
=======================

Get Landsat 8 Data from AWS public data sets. Includes functions for 
listing images and fetching them.

## Install

Dev version

```{r eval=FALSE}
devtools::install_github(c("ropenscilabs/getlandsat"))
```

```{r}
library("getlandsat")
```

```{r echo=FALSE}
lsat_cache_delete_all()
```


## List scenes

```{r}
(res <- lsat_scenes(n_max = 10))
```

## List scene files

```{r}
lsat_scene_files(x = res$download_url[1])
```

## Get an image

Returns path to the image

```{r}
lsat_image(x = "LC80101172015002LGN00_B5.TIF")
```

Another one

```{r}
lsat_image("LC80010032014272LGN00_B10.TIF")
```

### Caching

When requesting an image, we first check if you already have that image. If you do, 
we return the path to the file. If not, we get the image, and return the file path.

```{r message=TRUE}
lsat_image(x = "LC80101172015002LGN00_B5.TIF")
```

Note the message given.

See `?lsat_cache` for cache management functions.

## Visualize

```{r}
library("raster")
x <- lsat_cache_details()
img <- raster(x[[1]]$file)
plot(img)
```
